---
title : "In Class Exercise 1"
author: "Oytun Gungor"
date  : "2023-01-04"
output: html_document
---
## Import and install required libraries

```{r,message=FALSE}
install.packages("tidyverse")
install.packages("nycflights13")
library("tidyverse")
library("nycflights13")
library("ggplot2")
library("dplyr")
```

## Analyzing the data structure
```{r,message=FALSE}
head(planes) 
str(planes)
```
## Creating new df for looking relations between model year, seats number and motor type.
```{r,message=FALSE}
df_ys <- planes %>%
  select(year,seats,type)%>%
    arrange(desc(year))
## Cleaning na values
na.omit(df_ys)

ggplot(df_ys, aes(x = year, y= seats, color = type))+     
     geom_point()
```
According to the data and scatter plot, there is a correlation between seat number and product year. You can see that before the 1980' there is no plane with 200+ seat capability.

In addition to this, the capability of all single-engine and rotorcraft planes has under 100 seats. There is another correlation between moto-type and the number of seats.

As a summary you need big planes you need multi engine moto-type.

### Creating new df for looking relations between model year, seats number and engine type.

```{r,message=FALSE}
my_planes <- planes %>%
  select(year,engine,seats)%>%
  group_by(year)%>%
  arrange(engine)
na.omit(my_planes)
ggplot(my_planes, aes(x = year, y= engine,color = seats))+
  geom_point()
```

According to the data and plot, we can some insights about engine technology. There is inferences below

-   Turbo jet and turbo fan is using after 1980' in general
-   4 cycle engine was used once at middle of 1970'
-   Turbo jet and turbo fan technologies using by airlines companies
